---
title: "p8105_hw6_jh4324"
author: "Jiying Han"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)
library(rvest)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

This is my solution of homework 6

# Problem 1

Import and clean the data
```{r}
homicide_df = 
  read.csv("./data/homicide-data.csv", na =c("","NA","Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White","Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)

```


Start with one city
```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, data = baltimore_df, family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digit = 3)
```


Try this across cities

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state,term, OR, starts_with("CI")) 
```


Make the plot
```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```


# Problem 2

## Import the data
```{r }

# Check for missing data
anyNA(read.csv("./data/birthweight.csv"))

birthweight_df = 
  read.csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"
    ),
    frace = case_when(
      frace == 1 ~ "White", 
      frace == 2 ~ "Black", 
      frace == 3 ~ "Asian", 
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other", 
      frace == 9 ~ "Unknown"
    ),
    malform = case_when(
      malform == 0 ~ "absent", 
      malform == 1 ~ "present"
    ),
    mrace = case_when(
      mrace == 1 ~ "White", 
      mrace == 2 ~ "Black", 
      mrace == 3 ~ "Asian", 
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other"
    )
  ) %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) 

```

## Set two models 
```{r }
model1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
broom::tidy(model1)

model2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)
broom::tidy(model2)
```

## Propose a model

* 1. Predictor Selection - We use backward to build the model
We fit a regression using all predictors, and use AIC criterion for var selection, from which we choose the model with the smallest value.

```{r }
all_fit = lm(bwt ~ babysex + bhead + blength + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain,data = birthweight_df)
broom::tidy(all_fit) 

step(all_fit, direction='backward') %>% broom::tidy()
```

* 2. Get the final model
According to the result of first step, we can get some reasonable predictors, which can be added into the mode. Then we use these preditors to build the model.

```{r }
best_model = lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df)
broom::tidy(best_model)
```

* 3. Make a plot of the "best" model

```{r }
# a plot of model residuals against fitted values
plot = 
  birthweight_df %>% 
  modelr::add_residuals(best_model) %>% 
  modelr::add_predictions(best_model) %>% 
  ggplot(aes( x = pred, y =resid)) +
  geom_point(alpha = 0.3)

plot
```

Everything is centered around 0, and it makes sense, and most points are scatter around roughly prediction = 3200, but there are some departure towards left in prediction and some towards up in residuals, which means that if baby birth weight tends low, the residuals will become high.


## Compare these models

* 1. Cross Validation
```{r }
cv_df = 
  crossv_mc(birthweight_df, 100)

cv_df = 
  cv_df %>% 
  mutate(
    firmod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = birthweight_df)),
    secmod = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)),
    bestmod = map(.x = train, ~lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df))
  ) %>% 
  mutate(
    rmse_model1 = map2_dbl(.x = firmod, .y = test, ~rmse(model = .x, data =.y)),
    rmse_model2 = map2_dbl(.x = secmod, .y = test, ~rmse(model = .x, data =.y)),
    rmse_bestmodel = map2_dbl(.x = bestmod, .y = test, ~rmse(model = .x, data =.y))
  )
```


* 2. See the distribution of three models RMSE
```{r }
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse, color = model, fill = model)) +
  geom_violin() +
  stat_summary(fun = "median", color = "blue") +
  labs(
    x = "Model",
    y = "RMSE",
    title = "Distribution of three models' RMSE"
  )
```

From the plot, we can see that among three models, the model I made has the lowest RMSE, which means that this is a better model than other two models.

# Problem 3

Import the data
```{r }
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything()) 
 
```



## Analysis the samples

* 1. Build the function to get a sample
```{r }
# build the function to get a sample from dataset
boot_sample = function(df){
  sample_frac(df, replace = TRUE)
}
```


* 2. Build 5000 samples
```{r }
# get 5000 samples
set.seed(1)
boot_straps = 
  data_frame(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
    )
```


* 3. Explore the distribution and 95% CI
```{r }
# analyze the samples 
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(.x = strap_sample, ~ lm(tmax ~ tmin, data =.x)),
    results1 = map(models, broom::glance),
    results2 = map(models, broom::tidy)
  ) %>% 
  select(-strap_sample, - models)
```



```{r }
# distribution of estimated r squared

bootstrap_results %>% 
  select(strap_number,results1) %>% 
  unnest() %>% 
  select(strap_number, r.squared) %>% 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    x = "R squared",
    y = "Density",
    title = "Distribution of R squared"
  )
```
From the density plot, we can see that the most frequent value of R squared is roughly 0.913. And the distribution is a little bit right skew. But in general, it's symmetric and might follow normal distribution

```{r }
# 95% CI of R squared

bootstrap_results %>% 
  select(strap_number,results1) %>% 
  unnest() %>% 
  select(strap_number, r.squared) %>% 
  summarize(
    upper = quantile(r.squared, 0.025),
    lower = quantile(r.squared, 0.975)
) %>% 
  knitr::kable()
```


```{r include=FALSE}
# Distribution of log(beta0*beta1)
bootstrap_results %>% 
  select(strap_number,results2) %>% 
  unnest() %>% 
  select(term, estimate) %>% 
  pivot_wider(
    term:estimate,
    names_from = term, 
    values_from = estimate
    ) %>% 
  unnest() %>% 
  rename(intercept = "(Intercept)" ) %>% 
  mutate(
    log = log(intercept*tmin)
  ) %>% 
  ggplot(aes(x = log)) +
  geom_density()
```
From this plot, we can see that the distribution is symmetric and it's centered around 2.015. 

```{r include=FALSE}
# 95% CI of log(beta0*beta1)
bootstrap_results %>% 
  select(strap_number,results2) %>% 
  unnest() %>% 
  select(term, estimate) %>% 
  pivot_wider(
    term:estimate,
    names_from = term, 
    values_from = estimate
    ) %>% 
  unnest() %>% 
  rename(intercept = "(Intercept)" ) %>% 
  mutate(
    log = log(intercept*tmin)
  ) %>% 
  summarize(
    lower = quantile(log, 0.025),
    upper = quantile(log, 0.975)
  ) %>% 
  knitr::kable()
```

