---
title: "p8105_hw6_jh4324"
author: "Jiying Han"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

This is my solution of homework 6

# Problem 1

Import and clean the data
```{r}
homicide_df = 
  read.csv("./data/homicide-data.csv", na =c("","NA","Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White","Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)

```


Start with one city
```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, data = baltimore_df, family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digit = 3)
```


Try this across cities

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state,term, OR, starts_with("CI")) 
```


Make the plot
```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```


# Problem 2

## Import the data
```{r}
birthweight_df = 
  read.csv("./data/birthweight.csv", na.strings=c("")) %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"
    ),
    frace = case_when(
      frace == 1 ~ "White", 
      frace == 2 ~ "Black", 
      frace == 3 ~ "Asian", 
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other", 
      frace == 9 ~ "Unknown"
    ),
    malform = case_when(
      malform == 0 ~ "absent", 
      malform == 1 ~ "present"
    ),
    mrace = case_when(
      mrace == 1 ~ "White", 
      mrace == 2 ~ "Black", 
      mrace == 3 ~ "Asian", 
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other"
    )
  )
  

# Check for missing data
  sum(is.na(birthweight_df))
  
```

## Set two models 
```{r}
model1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
broom::tidy(model1)

model2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)
broom::tidy(model2)
```

## Propose a model

* 1. Predictor Selection - We use backward to build the model
we fit a regression using all predictors, and use AIC criterion for var selection, from which we choose the model with the smallest value.

```{r}
all_fit = lm(bwt ~ babysex + bhead + blength + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain,data = birthweight_df)
broom::tidy(all_fit) 

step(all_fit, direction='backward') %>% broom::tidy()
```

* 2. Get the final model

```{r}
best_model = lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df)
broom::tidy(best_model)
```

* 3. Make a plot of the "best" model

```{r}
# a plot of model residuals against fitted values
plot = 
  birthweight_df %>% 
  modelr::add_residuals(best_model) %>% 
  modelr::add_predictions(best_model) %>% 
  ggplot(aes( x = pred, y =resid)) +
  geom_point()
```

Everything is centered around 0, and it makes sense, and most points are scatter around roughly prediction = 3200, but there are some departure towards left in prediction and some towards up in residuals, which means that if baby birth weight tends low, the residuals will become high.


## Compare these models

* 1. Cross Validation
```{r}
cv_df = 
  crossv_mc(birthweight_df, 100)

cv_df = 
  cv_df %>% 
  mutate(
    firmod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = birthweight_df)),
    secmod = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)),
    bestmod = map(.x = train, ~lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df))
  ) %>% 
  mutate(
    rmse_model1 = map2_dbl(.x = firmod, .y = test, ~rmse(model = .x, data =.y)),
    rmse_model2 = map2_dbl(.x = secmod, .y = test, ~rmse(model = .x, data =.y)),
    rmse_bestmodel = map2_dbl(.x = bestmod, .y = test, ~rmse(model = .x, data =.y))
  )
```


* 2. See the distribution of three models RMSE
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse, color = model, fill = model)) +
  geom_violin() +
  stat_summary(fun = "median", color = "blue") +
  labs(
    x = "Model",
    y = "RMSE",
    title = "Distribution of three models' RMSE"
  )
```

From the plot, we can see that among three models, the model I made has the lowest RMSE, which means that this is a better model than other two models.

# Problem 3

Import the data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything()) 
 
```




